---
title: "Workshop Manuscript"
author: "Attendees"
date: "July 11, 2019"
output: pdf_document
---

```{r setup, echo = FALSE}
#Moves directory up two levels, by default the .rmd knit will be in the same directory as where the file is located. But we want to reference scripts in our script directory, so we need to go back to the project root folder.
setwd('../..')
```

## Introduction

In 2010, the National Health Survey on Drug use and Health (NSDUH) primarily measures the prevalence and correlates of drug use in the United States.  The information collected was designed to learn population level use of illicit drugs, alcohol, and tobacco among members of United States households aged 12 and older. The survey covers substance use history, treatment, and perceived need for treatment, including questions from the DSM IV. Respondents were also asked about personal family income sources and amounts, and health care access. For this study, we were interested in comparing the characteristics of a subgroup of youth (age 12-17) respondents who are currently receiving counseling for mood disorders.

Growing up with a diagnosed mood disorder can significantly increase the changes of the youth trying a cigarette, and continuing to smoke. 

## Methods

For this study we will collaborate with fellow workshop attendees to determine if there is an effect of having tried a cigarette on overall health rating from the NSDUH 2010 data. Since we are confident that we will find an effect, we will be looking at differences in self-reported gender as well. To address this problem we will run a simple between-groups ANOVA, comparing the mean effects of having tried a cigarette on self-reported health. We believe that this sub sample of survey respondents who have been treated for a mood disorder and have tried a cigarette will report a lower index of self-reported overall health. 

## Results

```{r result, echo = FALSE}
#We only need one chunk to import all of our study results.
#Since our other scripts will reference the import script to generate the values, we do not need to source it here.

#Read in the table script, all variables from this script are now in the working environment.
source("script/demographic_table.R", local = TRUE)
#Read in the ANOVA script, all variables from this script are now in the working environment.
source("script/ANOVA.R", local = TRUE)
#Read in the mean plot script, all variables from this script are now in the working environment.
source("mean_plot.R", local = TRUE)
```

### Sample Demographics
Table 1 shows us the characteristics of this subgroup of youth seeking clinical support for a mood disorder.

### ANOVA


### Mean Plots


